%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Agentic AI } % Job title
    {Inria (National Institute for Research in Digital Science and Technology)} % Organization
    {Bordeaux, France} % Location
    {Mar. 2026 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered a framework-less AI agent from first principles to support and accelerate PhD research workflows.}
        \item {Designed and implemented a custom Retrieval-Augmented Generation (RAG) pipeline alongside diverse tool-use functionalities to enhance the agent's reasoning and execution capabilities.}
        \item {Designed and implemented an interactive web interface to facilitate seamless user interaction with the AI agent.}
        \item {Conducted a rigorous comparative benchmarking of various open-source LLMs deployed locally}
      \end{cvitems}
    }

  \cventry
    {Research intern in RL} % Job title
    {Karunya University} % Organization
    {Coimbatore, Tamil Nadu, India} % Location
    {Jun. 2025 - Sep. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Designed and implemented two distinct navigation approaches for an autonomous indoor hospital robot: a classical deterministic path-planning algorithm and a reinforcement learing-based navigation model.}
        \item {Conducted a comparative analysis between the algorithmic and reinforcement learning models.}
        \item {Successfully deployed and optimized the reinforcement learning model onto an embedded Raspberry Pi}
      \end{cvitems}
    }

  % \cventry
  %   {Data analyst intern} % Job title
  %   {Rio Tinto} % Organization
  %   {Fort-Dauphin, Madagascar} % Location
  %   {Jun. 2024 - Jul. 2024} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %      \item {Analyzed and processed multi-departmental enterprise data to support cross-functional business intelligence}
  %     \end{cvitems}
  %   }

\end{cventries}
